Beyond ``Horizontal'' and ``Vertical'':\\ The Welfare Effects of Complex Integration\tnoteref{t1}

### 2024-09-30 doc/TrashData.tex
minor edits to get the code to run on Board machines. These figures use a different strategy for fixing either upstream or downstream pre-merger prices in the antitrust package than before. However, the results look the same as the first method.
Incorporated Gloria's 11/2 edits to document and TrashData.tex. First Full run of simulations on FRB machine. inter-quartile ranges line up almost perfectly, min and maxes are very close. Examined pictures and they look the same as well. Fixed minor issues with extra row in sumtable.
reran trashsims to accomodate changes for JIE submission.
modified pi

\begin{table}

\caption{\label{tab:trashdata}Republic/Santek Merger Simulation Inputs. Prices and margins are reported in dollars, while volume is reported in thousands of pounds.}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{rrccccc}
\toprule
Disposal Firm & Collection Firm & Volume & Disposal Price & Disposal Margin & Collection Margin & Collection Price\\
\midrule
Republic & Republic & 165 & 42 & 0 & 44 & 179\\
\cmidrule{1-7}
 & Republic & 34 & 36 & 20 &  & 173\\

 & Santek & 218 & 16 & 0 &  & 134\\

 & WM-ADS & 30 & 36 & 20 &  & 221\\

\multirow{-4}{*}{\raggedleft\arraybackslash Santek} & Regional & 30 & 36 & 20 &  & 221\\
\cmidrule{1-7}
 & Republic & 19 & 25 & 14 &  & 162\\

 & WasteConn & 48 & 11 & 0 &  & 110\\

 & WM-ADS & 17 & 25 & 14 &  & 210\\

\multirow{-4}{*}{\raggedleft\arraybackslash WasteConn} & Regional & 17 & 25 & 14 &  & 210\\
\bottomrule
\end{tabular}}
\end{table}

>>>>

\caption{\label{tab:trashdata}Republic/Santek Merger Simulation Inputs. Volume is reported in thousands of pounds, while prices and margins are reported in dollars.}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{rrccccc}
\toprule
Disposal Firm & Collection Firm & Volume & Disposal Price & Disposal Margin & Collection Margin & Collection Cost\\
\midrule
Republic & Republic & 165 & 42 & 0 & 44 & 93\\
\cmidrule{1-7}
 & Republic & 34 & 36 & 20 &  & 93\\

 & Santek & 218 & 16 & 0 &  & 74\\

 & WMADS & 30 & 36 & 20 &  & 148\\

\multirow{-4}{*}{\raggedleft\arraybackslash Santek} & Regional & 30 & 36 & 20 &  & 148\\
\cmidrule{1-7}
 & Republic & 19 & 25 & 14 &  & 93\\

 & WasteConn & 48 & 11 & 0 &  & 63\\

 & WMADS & 17 & 25 & 14 &  & 148\\

\multirow{-4}{*}{\raggedleft\arraybackslash WasteConn} & Regional & 17 & 25 & 14 &  & 148\\
\bottomrule
\end{tabular}}
